### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

% Reviewer 1:
 > My comments and concerns have been addressed in detail. Thank you.

% Reviewer 3:

> I believe that most issues highlighted previously have been 
  addressed adequately. In particular, the structure of the 
  revised manuscript has been improved significantly. 
  I still found the paper challenging to read, but this is 
  largely due to the complexity of the biological system and 
  the necessary encoding details presented in the manuscript.

  Pt #1:
-------- Handle by Mukund --------------
  One point that I think requires further attention is the 
  motivation for using connectedness and the explanation of 
  this property, which is at the core of the proposed approach. 
  I did not find the additional explanations provided in the 
  response and the revised manuscript sufficient. Simply stating 
  that "The graph k-connectedness furnishes precisely" a test to 
  determine if information is missing from the model and that 
  "If the data […] does not have a certain degree of connectivity, 
  this implies that some biological data has been missed" does not 
  justify connectedness as a fundamental and required biological 
  property that all valid models should respect. The intuition of 
  connectedness as a robustness property provided elsewhere in the 
  manuscript helps but it is still not clear what evidence supports 
  the fact that VTSs are indeed robust. In addition, the problem as 
  formulated does not seem to seek the most robust networks as 
  explained in the following.

@@

  Authors response: We now state the equivalence of our 
  steady state condition and homeostasis of compartments
  only in section 2.3.2.

  > There is overlap in the 3rd and 6th paragraphs of 
    the 'Related Work' section, which refer to the use 
    of SAT/SMT in GRNs.

  Authors response: The use of SAT/SMT in GRN is presented
  in two different context (non-overlapping references). 
  The third paragrah points to general use of SAT/SMT 
  solvers in GRN, whereas 6th paragraph refers to a specific
  use (synthesis). We have updated the text to improve this
  distinction.

Minor points:

  > Small typos / grammatical errors. There are a number 
    of these throughout the text, some of which are listed 
    below (this is not exhaustive, so I recommend carefully 
    reading the manuscript to ensure clarity):

  > Page 2, lines 11-12: Understanding how membrane traffic 
    functions *is*, therefore,…
  Authors response: Correction incorporated.

  > Page 2, line 13: Cell biologists have made… (not 'The')
  Authors response: Correction incorporated.

  > Page 3, line 14: "…parts of the traffic system that 
    *are* unchanging…"
  Authors response: Correction incorporated.

  > Page 4, line 6: "We also worked on the synthesis of the 
    unknown pieces *that* may be assisted…" Just after this: 
    "In the work, we developed *an* encoding for the 
    synthesis problem."
  Authors response: Both corrections are incorporated.

  > Figure 1 legend, line 44: "typical" not "typic"
  Authors response: Corrections incorporated 
  (typic was in caption of Fig. 1).

  > Page 7, line 11: "We have tried to capture important 
    *aspects* of *the* Rothman-Schekman-Sudhof (RSS) model 
    of *the* vesicle…" Also "components" not "component" 
  Authors response: Both corrections are incorporated.

  > Example 1, line 40: "labels are a set of molecules"
  Authors response: Correction incorporated.

  > Example 2, line 36: "Fig. 3b presents its complete output VTS."
  Authors response: Correction incorporated.

  > Page 14, line 16: "We will also seek *to answer* two 
    kinds of questions, *given* the property."
  Authors response: Both corrections are incorporated.

  > Page 15, line 14: "to ensure the k to be the least one" 
    -> "to ensure that k is minimized"
  Authors response: Correction incorporated.

  > Page 22: "The specification for *the* universal condition 
   *described in* Section 5" 
  Authors response: Both corrections are incorporated.

### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

We would like to thank the reviewers for their very detailed and
helpful comments. In the following, we ellaborate on how we addressed
the feed in the revised version of our paper.

@@

  > There is overlap in the 3rd and 6th paragraphs of 
    the 'Related Work' section, which refer to the use 
    of SAT/SMT in GRNs.

  Authors response: The use of SAT/SMT in GRN is presented
  in two different context (non-overlapping references). 
  The third paragrah points to general use of SAT/SMT 
  solvers in GRN, whereas 6th paragraph refers to a specific
  use (synthesis). We have updated the text to improve this
  distinction.

Minor points:

  > Small typos / grammatical errors. There are a number 
    of these throughout the text, some of which are listed 
    below (this is not exhaustive, so I recommend carefully 
    reading the manuscript to ensure clarity):
  Authors response: We thank the reviewer for pointing these 
  out. We have corrected the listed errors and performed 
  multiple careful readings fixing other errors that we found.

### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

% Reviewer 3:

> I believe that most issues highlighted previously have been 
  addressed adequately. In particular, the structure of the 
  revised manuscript has been improved significantly. 
  I still found the paper challenging to read, but this is 
  largely due to the complexity of the biological system and 
  the necessary encoding details presented in the manuscript.

  Pt #1:
-------- Handle by Mukund --------------
  One point that I think requires further attention is the 
  motivation for using connectedness and the explanation of 
  this property, which is at the core of the proposed approach. 
  I did not find the additional explanations provided in the 
  response and the revised manuscript sufficient. Simply stating 
  that "The graph k-connectedness furnishes precisely" a test to 
  determine if information is missing from the model and that 
  "If the data […] does not have a certain degree of connectivity, 
  this implies that some biological data has been missed" does not 
  justify connectedness as a fundamental and required biological 
  property that all valid models should respect. The intuition of 
  connectedness as a robustness property provided elsewhere in the 
  manuscript helps but it is still not clear what evidence supports 
  the fact that VTSs are indeed robust. In addition, the problem as 
  formulated does not seem to seek the most robust networks as 
  explained in the following.

  > I also found the formulation of the main problems with respect 
    to connectedness somewhat confusing. For example, in Sec. 5.1.1 
    and Sec. 5.1.2 the problems are formulated as a search for VTS G 
    such that G is not k-connected. Yet, Sec. 5.1 specifies that 
    "In case the formula is satisfiable the procedure terminates and 
    we report the value of k", which seems contradictory. Finally, 
    it is not clear why the goal is to find the minimum graph 
    connectivity, given that larger connectivity corresponds to a 
    more robust network. I was expecting an approach involving 
    incrementing k to find the smallest value that makes the formula 
    unsatisfiable, thus identifying the maximum graph connectedness 
    possible for a given VTS with all other constraints being 
    satisfied. However, to the best of my understanding, this is not 
    what the paper is currently proposing, or else further  
    clarifications are needed.

  Authors response: Sec. 5 gives a high-level explanation of 
  the problems and present a formal search statement 
  (implementation based). We have now rewritten the parts of 
  the text to address the clarity and the distinction between 
  high-level overview and the implementation. 
  We have also removed the specific search problems (as suggested 
  by Reviewer #3 in the first revision) for clarity and accessibility.

### 2019-09-09 papers/journal/problem.tex
Added additional points

We employ two techniques to examine the existential condition. 
%
First, using the BMC and second using SMT solving.
%
Throughout the paper, we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
%
Here, we present both the $\fbmc$ and $\fsmt$ search problem for the existential condition.

\subsubsection{$\fbmc$ search problem.}
For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth $w$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected, within $w$ depth of unwinding.

\subsubsection{$\fsmt$ search problem.}
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and
$G$ is not $k$-connected.

@@

%\ankit{This is a dummy template. need a rewrite.} 
\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.

>>>>

We employ two techniques to examine the existential condition. 
%
First, using the BMC and second using SMT solving.
%
Throughout the paper, we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
%
%Here, we present both the $\fbmc$ and $\fsmt$ search problem for the existential condition.
%
%\subsubsection{$\fbmc$ search problem.}
%For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth $w$,
%we are searching for well-structured, stable, and well-fused VTS
%$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
%$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected, within $w$ depth of unwinding.    
%
%\subsubsection{$\fsmt$ search problem.}
%For a given $k$, size $\nu$, and molecule number $\mu$,
%we are searching for well-structured, stable, and well-fused VTS
%$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
%$|\nodes| = \nu$, $|\mols| = \mu$, and
%$G$ is not $k$-connected.

@@

%%\ankit{This is a dummy template. need a rewrite.} 
%\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
